### 2019-02-21 sections/abstract.tex
Removed fixme
add todo in abstract

Software that models how people work is omnipresent in todays society.
Current languages and frameworks are limited in flexibility and lack the proper level of abstraction.
Task-Oriented Programming (\TOP) is a programming paradigm that aims to provide the desired level of abstraction while still being expressive enough to describe real world collaboration.
It prescribes a declarative programming style to specify multi-user workflows.
Workflows can be higher-order.
They communicate through typed values on a local or global level.
Such specifications can be turned into interactive applications for different platforms,
supporting collaboration during execution.

@@

\fixme{Why?}

>>>>

Software that models how people work is omnipresent in todays society.
Current languages and frameworks are limited in flexibility and lack the proper level of abstraction.
Task-oriented programming (\TOP) is a programming paradigm that aims to provide the desired level of abstraction while still being expressive enough to describe real world collaboration.
It prescribes a declarative programming style to specify multi-user workflows.
Workflows can be higher-order.
They communicate through typed values on a local or global level.
Such specifications can be turned into interactive applications for different platforms,
supporting collaboration during execution.

@@

\fixme{Add Knowledge, Grounding and Importance}
